%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{deedy-resume-openfont}
\newcommand\tab[1][0.5cm]{\hspace*{#1}}
\usepackage{fancyhdr}
\usepackage{hyperref}

\pagestyle{fancy}
\fancyhf{}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \lastupdated % hide last updated date

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{minipage}{0.6\textwidth}
    \namesection{Mao-Lin}{Wang}{}
\end{minipage}
\hfill
\begin{minipage}{0.4\textwidth}
    \begin{tightemize}
        \item[] \urlstyle{same}\href{https://focaaby.com/}{https://focaaby.com/}
        \item[] +886-926-633005 | \href{mailto:focaaby@gmail.com}{focaaby@gmail.com}
    \end{tightemize}
\end{minipage}

\par\noindent\rule{\textwidth}{0.5pt} % horizontal line

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{1\textwidth}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SUMMARY
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Summary}
\begin{summary}
  Experienced DevOps engineer with over five years of expertise in Kubernetes, CI/CD, and leadership. Demonstrated ability to solve complex infrastructure problems independently.
\end{summary}

\section{Skill}
\vspace{\topsep}
\begin{tightemize}
    \item \textbf{\emph{Linux}} 10+ years | System admin and architecture including building, managing, maintaining, monitoring, and tuning, SRE.
    \item \textbf{\emph{Education}} 10+ years | Training, study circle host, workshops, companies, In University school(Teaching assistant since 2013).
    \item \textbf{\emph{DevOps}} 8+ years | Distributed systems, Container, Docker, Kubernetes, GitHub/GitLab, Ansible, Prometheus, AWS Infra.
    \item \textbf{\emph{Software Engineering}}  8+ years | Frontend, Blockchain, JavaScript (Vanilla JS, Node.js).
\end{tightemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{Amazon Web Services}
\descript{Cloud Support Engineer II/I/Associate}
\null\hfill\location{Jul 2019 - present | Ireland / Taiwan}
\begin{tightemize}
    \item Mandarin Engineer of the Yea(2022, EMEA team).
    \item Certiﬁcation of AWS EKS Subject Matter Expert.
    \item Creator of EKS operations helper(Tampermonkey script) to streamline workﬂow.
    \item Mentor of DevOps and Security domain services.
    \item Interviewer of DevOps domain.
    \item Maintainer of Accessibility and Usability of EMEA language and Mandarin team pages in internal Knowledge Management system.
    \item Troubleshooting and resolving business critical issues for customers in various industries about Kubernetes and CI/CD domain services.
\end{tightemize}
\sectionsep

\runsubsection{Bridgewell}
\descript{DevOps \& Project Manager}
\null\hfill\location{Sep 2018 – June 2019 | Taipei, Taiwan}
\begin{tightemize}
    \item Spearheaded the building of Kubernetes from scratch.
    \item Streamlined the CI/CD pipeline through GitLab templates optimization.
    \item Optimized and reduced overall product deliverable package size by 80\% through Docker image optimization.
    \item Led the implementation of an internal financial system as project manager and frontend engineer, collaborating with multiple departments to ensure successful delivery of project requirements.
\end{tightemize}
\sectionsep

\runsubsection{Fubon Financial Holding Co., Ltd - FinTech office}
\descript{Internship}
\null\hfill\location{Sep 2017 – Jan 2018 | Taipei, Taiwan}
\begin{tightemize}
    \item Developed multiple proof-of-concept web3 applications utilizing Ethereum and web3j.
\end{tightemize}
\sectionsep

\runsubsection{Taiwan Stock Exchange}
\descript{Research Assistant}
\null\hfill\location{May 2017 – Dec 2017 | Taipei, Taiwan}
\begin{tightemize}
    \item Revamped a high-availability infrastructure with Docker containers to mitigate the single point of failure (SPOF) issue with Kafka and Zookeeper, ensuring efficient high-throughput message queue operations.
    \item Automated the CI/CD pipeline for testing by implementing an Ansible playbook with different environment variables.
\end{tightemize}
\sectionsep

\runsubsection{Cheng Uei Precision Industry Co., Ltd}
\descript{Research Assistant}
\null\hfill\location{Nov 2016 – Aug 2017 | Taipei, Taiwan}
\begin{tightemize}
    \item Implemented an IFTTT (if this, then that) process.
    \item Introduced openHAB2 environment and tested the MQTT broker with AWS IoT service.
\end{tightemize}
\sectionsep

\runsubsection{Imonology Inc.}
\descript{Front-end Internship}
\null\hfill\location{Jul 2015 – Jun 2016 | Nantou, Taiwan}
\begin{tightemize}
    \item Implemented the Hydra system, an IoT integration and automation system utilizing jQuery as the frontend technology.
    \item Implemented the React.js framework and refactored the single-page application using React.js.
\end{tightemize}
\sectionsep

\runsubsection{Department of Information Management, NCNU}
\descript{System Admin}
\null\hfill\location{June 2014 – Sep 2016 | Nantou}
\begin{tightemize}
    \item Converted all physical machines into virtual machines and seamlessly migrated them into the VMware vSphere environment.
    \item Migrated from an Apache Web Server to Nginx, setting up the Nginx server with HTTP/2 and SSL, resulting in a 60% improvement in page-loading time.
    \item Developed an automated deployment script for CMS platforms (such as WordPress or Joomla).
\end{tightemize}



\end{minipage}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     PAGE TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\hfill
\begin{minipage}[t]{1\textwidth}


\section{Experience (Organization / Community)}
\runsubsection{MOLi - Makers' Open Lab for Innovation}
\descript{Event Coordinator}
\null\hfill\location{2015 – July 2019 | Nantou, Taiwan / Remote}
\vspace{\topsep}
\begin{tightemize}
    \item Coordinated over 10 MOLiDay sharing events, featuring various topics such as technology, education topics.
    \item Managed the organization's Facebook fan page, utilizing content creation and social media marketing strategies to engage with followers and promote events.
\end{tightemize}
\hspace{12pt}\keyword{KKTIX: \urlstyle{same}\href{https://moli.kktix.cc/}{https://moli.kktix.cc/}}
\sectionsep


\runsubsection{MOLi - Online study circle}
\descript{Host}
\null\hfill\location{Nov 2020 – May 2022 | Remote}
\begin{tightemize}
    \item \urlstyle{same}\href{https://lsa.moli.rocks/study-circle/docs/2020-11-07}{2020 - 《鳥哥的 Linux 私房菜：基礎學習篇》}
    \item \urlstyle{same}\href{https://lsa.moli.rocks/study-circle/docs/docker-1}{2021 - 《Docker in Action 2nd edition》}
    \item \urlstyle{same}\href{https://lsa.moli.rocks/study-circle/docs/k8s-1}{2022 - 《Kubernetes in Action》}
\end{tightemize}
\sectionsep

\runsubsection{University Graduate Association of National Chi Nan University}
\descript{Vice President}
\null\hfill\location{June 2014 – May 2015 | Nantou, Taiwan}
\begin{tightemize}
    \item Persuaded the university association to collaborate for the event.
    \item Planned and executed the graduation party successfully, with over 250 attendees.
    \item Sourced a graduation yearbook manufacturer and coordinated the graduation photo event schedule.
\end{tightemize}
\sectionsep

\runsubsection{Department of Information Management, NCNU}
\descript{President of Student Association}
\begin{tightemize}
    \item Served as the Student Representative for the Curriculum Committee. \null\hfill\location{June 2012 – May 2013 | Nantou}
    \item Successfully planned and executed the inaugural alumni sports event for 2 weeks, which drew a turnout of over 100 participants.
\end{tightemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     CERTIFICATE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Certificate}

\runsubsection{\urlstyle{same}\href{https://www.credly.com/earner/earned/badge/935959f7-a8b7-4acf-91ef-0cff90eadb5f}{Certified Kubernetes Administrator(CKA)}}
\descript{by The Linux Foundation}
\null\hfill\location{Dec 2021 - Dec 3 2024}
\runsubsection{\urlstyle{same}\href{https://www.credly.com/badges/75c12266-f115-417e-8876-d43ee5e747cf/linked_in_profile}{EKS Subject Matter Expert}}
\descript{by AWS Support Engineering}
\null\hfill\location{Apr 2022 - present}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Projects}

\runsubsection{Taiwan EBook Search}
\descript{Frontend \& DevOps}
\null\hfill\location{Dec 2017 – present | Remote}
\begin{tightemize}
    \item Utilized Vue.js to fetch backend crawler API and search cross-platform information about eBook prices, authors, etc.
    \item Implemented GitHub Action for deploying Vue.js static webpage to GitHub Pages.
\end{tightemize}
\hspace{12pt}\keyword{GitHub: \urlstyle{same}\href{https://github.com/Taiwan-Ebook-Lover/Taiwan-Ebook-Lover.github.io}{https://github.com/Taiwan-Ebook-Lover/Taiwan-Ebook-Lover.github.io}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PUBLICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Publications}

\runsubsection{2022 iThome 鐵人賽}
\descript{DevOps 組優選}
\null\hfill\location{2020 - 2022 | Remote}
\begin{tightemize}
    \item 那些文件沒告訴你的 AWS EKS 系列 - \urlstyle{same}\href{https://ithelp.ithome.com.tw/users/20151040/ironman/5059}{https://ithelp.ithome.com.tw/users/20151040/ironman/5059}
\end{tightemize}
\sectionsep

\runsubsection{MOLi - Online study circle}
\descript{Collaborative notes}
\null\hfill\location{Dec 2022 | Remote}
\begin{tightemize}
    \item Webpage - \urlstyle{same}\href{https://lsa.moli.rocks/study-circle/docs/}{https://lsa.moli.rocks/study-circle/docs/}
    \item HackMD - \urlstyle{same}\href{https://hackmd.io/@ncnu-opensource/linux-study-circle/}{https://hackmd.io/@ncnu-opensource/linux-study-circle/}
\end{tightemize}
\sectionsep

\runsubsection{NCNU OpenSource}
\descript{Collaborative notes}
\null\hfill\location{2014 - present | Remote}
\begin{tightemize}
    \item GitHub - \urlstyle{same}\href{https://github.com/NCNU-OpenSource}{https://github.com/NCNU-OpenSource}
    \item HackMD - \urlstyle{same}\href{https://hackmd.io/@ncnu-opensource/book}{https://hackmd.io/@ncnu-opensource/book}
\end{tightemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education}

\subsection{Master of Information Management}
\descript{National Taiwan University of Science and Technology}
\null\hfill\location{Sep 2016 - Aug 2018 | Nantou, Taiwan}
\thesis{On the Design and Implementation a Logging Management System that Satisfying Common Criteria Security Auditing Requirements with the Blockchain Technology}
\keyword{Keywords: Common Criteria, Security Auditing, Blockchain, Smart Contract, Hypereledger}

\vspace{\topsep}
\subsection{Bachelor of Information Management}
\descript{National Chi Nan University}
\null\hfill\location{Sep 2011 - Aug 2016 | Taipei, Taiwan}
\thesis{On the Design and Implementation Reaction Mechanisms of a Intrusion Detection and Prevention System in Linux Kernel-Level }
\keyword{Keywords: Virtual Machine, Virtual Machine Monitor, Intrusion Detection and Prevention System, Linux Kernel}
\end{minipage}

\end{document}  \documentclass[]{article}
