%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Jerry}{Wang}{ \urlstyle{same}\href{https://focaaby.github.io/}{https://focaaby.github.io/}\\
+886-926-633005 | \href{mailto:focaaby@gmail.com}{focaaby@gmail.com}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.45\textwidth}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{Fubon Financail FinTech Office}
\descript{| FinTech Intern}
\location{Sep 2017 – Jan 2018 | Taipei, Taiwan}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
    \item Building Decentralized Application with Ethereum and web3j.
\end{tightemize}
\sectionsep

\runsubsection{Taiwan Stock Exchange Corporation}
\descript{| Research Assistant}
\thesis{A research of boosting consistency and safety of system in software-defined infrastructure}
\location{May 2017 – Dec 2017 | Taipei, Taiwan}
\begin{tightemize}
    \item Redesign service architectures with microservices on Docker to avoid single point of failure and provide high availability.
    \item Design a CI/CD workflow to automatic test environment parameters with Ansible script.
    \item Set up a high throughput architectures with Kafka and Zookeeper cluster on Docker.
\end{tightemize}
\sectionsep

\runsubsection{Foxlink FPC}
\descript{| Research Assistant}
\thesis{IoT 2.0 smart application platform}
\location{Nov 2016 – Aug 2017 | Taipei, Taiwan}
\begin{tightemize}
    \item Design a IFTTT(if this, then that) workflow.
    \item Set up a  openHAB 2 environment and testing MQTT broker server on AWS IoT service.
\end{tightemize}

\runsubsection{Imonology}
\descript{| Front-End Engineering Intern }
\location{Jul 2015 – Jun 2016 | Nantou, Taiwan}
\begin{tightemize}
    \item A Integrated system of monitoring: use jQuery with backend API at the early stage, reactor code with React.js framework.
\end{tightemize}
\sectionsep

\runsubsection{NCNU Department of Information of Management}
\descript{| System   Administrator }
\location{June 2014 – Sep 2016 | Nantou, Taiwan}
\begin{tightemize}
    \item Converte all physical machines into virtual machines and migrate into VMware vSphere environment.
    \item Migrate from an Apache Web Server to Nginx, set up nginx with HTTP/2 and SSL, saved 60\% page-loading time.
    \item Created a automatic delpoyment CMS(Wordpress or Joomla) script.
\end{tightemize}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Awards}

\runsubsection{IOT SANDBOX Wargame}
\descript{| 1st place }
\location{May 2 2018 - May 3 2018| Yilan, Taiwan}
\descript{National Center for High-performance Computing}
\thesis{Team: Hsieh-Jia-Ko}

\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage}
\hfill
\begin{minipage}[t]{0.5\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}

\subsection{Master of Information Management}
\descript{National Taiwan University of Science and Technology}
\location{Sep 2016 - Aug 2018 | Taiwan}
\thesis{On the Design and Implementation a Logging Management System that Satisfying Common Criteria Security Auditing Requirements with the Blockchain Technology}
\keyword{Keywords: Common Criteria, security auditing, blockchain, smart contract, Hypereledger}

\vspace{\topsep}
\subsection{Bachelor of Information Management}
\descript{National Chi Nan University}
\location{Sep 2011 - Aug 2016 | Taiwan}
\thesis{On the Design and Implementation Reaction Mechanisms of a Intrusion Detection and Prevention System in Linux Kernel-Level }
\keyword{Keywords: Virtual Machine, Virtual Machine Monitor, Intrusion Detection and Prevention System, Linux Kernel}

\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Personal Project}

\runsubsection{Taiwan EBook Search}
\descript{| Web }
\location{Dec 2017 – Now | Taipei, Taiwan}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
    \item Use Vue.js fetch backend crawler API to search cross-platform information of Ebooks prices, author and etc.
    \item Automatically deploy GitHub Pages with Travis CI.
\end{tightemize}

\runsubsection{Blockchain Voting Systems}
\descript{| FrontEnd + Backend + Smart Contract}
\location{Feb 2017 – Jun 2017 | Taipei, Taiwan}
\begin{tightemize}
    \item Building a private multi-node Ethereum blockchain with Docker.
    \item Backend and FrontEnd by using Node.js and Vue.js .
\end{tightemize}

\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}

\begin{minipage}[t]{0.45\textwidth}
    \subsection{FrontEnd/Backend}
    \vspace{\topsep}
    \begin{tightemize}
        \item React.js
        \item Javascript
        \item ECMAScript 6
        \item HTML/CSS/SCSS
        \item Node.js
    \end{tightemize}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}
    \subsection{Operating System}
    \vspace{\topsep}
    \begin{tightemize}
        \item Ubuntu
        \item macOS
    \end{tightemize}
\end{minipage}

\vspace{\topsep}
\begin{minipage}[t]{0.45\textwidth}
    \subsection{Linux}
    \vspace{\topsep}
    \begin{tightemize}
        \item Shell Script
        \item Nginx
        \item Docker
        \item Ansible
    \end{tightemize}
\end{minipage}


\end{minipage}
\end{document}  \documentclass[]{article}
